Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-08 02_Paper/paper.tex
introduction

% With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production. This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.

The quality control (QC) of production processes and products is one fundamental part of general quality management. It contains the measures and activities needed to fulfill specific quality requirements.
% According to Illés, there are three established tools and methods of quality control:
% The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC) \cite{illes2017new}. 
According to Illés, there are diverse established tools and methods of quality control. Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}. In this paper, we focused on the methods related to the QC at the product level.

@@

The quality characteristics of a product can be classified as variables or attributes.
Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data. This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place. With that in mind, predictive quality control is a promising solution.

@@

This paper is divided in 6 sections:
\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

\section{Related Works} % 1 Page

@@

Applications that combine PA with QC might improve the current QC processes. By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.

@@

By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation. To do so, we need to select the right testing platform. It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary 
In our work, we applied a case-based research approach \cite{yin2017case} 
% to answer the research question \AP{what research question?}.
for our implementation.
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page

@@

\section{Experiments}

@@

\section{Conclusion}

@@

\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv
\bibliography{bib}

>>>>

For companies aiming at quality leadership, the final quality of any goods produced is vital for market success. That is why it is highly important for companies to ensure that every product meets the expected requirements.
The quality control (QC) of production processes and products is one fundamental part of general quality management. It contains the measures and activities needed to fulfill specific quality requirements.
According to Illés, there are diverse established tools and methods of quality control. Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}. In this paper, we focused on the methods related to the QC at the product level.

@@

The quality characteristics of a product can be classified as variables or attributes.
Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data. This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place. 
% With that in mind, predictive quality control is a promising solution.

@@

The aim of this paper is to implement a functional predictive model in quality assurance for an assembly process in a controlled environment. Within the scope of the implementation, we compare three different ML models accuracy, as well as their plausibility at industrial applications. 
As result, we expect to to decrease the gap in literature on this research area, as well as to describe the based of our experiences for future works by describing the lesson learned during this implementation.
In our work, we applied a case-based research approach \cite{yin2017case} 
% to answer the research question \AP{what research question?}.
for our implementation.
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed

Our paper is structured as follow. Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production. Section.~\ref{sec:democell} describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation. Section.~\ref{sec:ML} explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree. Section.~\ref{sec:experiment} describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing. Finally Section.~\ref{sec:conclusion} express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.

\section{Related Works} \label{sec:related_works}% 1 Page

@@

Applications that combine PA with QC might improve the current QC processes. By employing machine learning (ML) techniques, see Sec.~\ref{sec:ML}, together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.

@@

% By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation. To do so, we need to select the right testing platform. It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary.
% In our work, we applied a case-based research approach \cite{yin2017case} 
% % to answer the research question \AP{what research question?}.
% for our implementation.
% One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.

\section{The case industry 4.0 demonstration cell}  \label{sec:democell}% (taken from title) % 3/4 Page

@@

\section{Experiments} \label{sec:experiment}

@@

\section{Conclusion} \label{sec:conclusion}

@@

\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv %IEEEtran
\bibliography{bib}
